R Notebook

### 2022-04-29 Code/Simulation.Rmd
code to create combined plots

@@

# Save the histogram figure
ggsave(filename = "hist_fitted.pdf", plot = hist_fitted, path = "../Manuscript", height = 2.1, width = 6)

data_new <- results                              # Replicate data
data_new$histogram <- factor(data_new$histogram,      # Reordering group factor levels
                         levels = c("Naive", "Parametric", "Babu"))

# Generate histograms plot
hist_fitted <- ggplot(data_new) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")
hist_fitted
```

@@

# Set variables
n <- 100
ar <- 0.5
counter <- 0
nrep <- 500
B <- 100
mean <- 0
sd <- 1

@@

@@

# Set variables
n <- 100
counter <- 0
nrep <- 100
B <- 100
ma <- 0.5
mean <- 0
sd <- 1

@@

# Set variables
n <- 100
counter <- 0
nrep <- 100
B <- 100
ar <- 0.5
ma <- 0.3
mean <- 0
sd <- 1

@@

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(order = c(2, 0, 0), 
                                                           ar = c(b1, b2)),
                                                      rand.gen=rnorm,
                                                      sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)),
                                                      n = n))$p.value)

@@

# Set variables
n <- 100
counter <- 0
nrep <- 100
B <- 100
b1 <- 0.5
b2 <- 0.3
mean <- 0
sd <- 1

@@

# Set variables
n <- 100
rho <- 0.5
counter <- 0
nrep <- 100
B <- 100
shape <- 3
scale <- 1

@@

# Set variables
n <- 100
rho <- 0.5
counter <- 0
nrep <- 100
B <- 100
loc <- 0
shape <- 0.2
scale <- 1

@@

```{r Copula FD}
test_copula_D <- function(x, dist, B) {

@@

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), "pnorm", B = B))
counter <- 0

@@

# Create a master data_frame with all the results
histogram <- c(rep("Copula", nrep), rep("Naive Parametric", nrep), rep("Super Naive", nrep))
p_values <- c(pvals_copula, pvals_parametric, pvals_naive)
results <- data_frame(p_values, histogram)
save(results, file = "results_copula.RData")

@@

# Save the histogram figure
ggsave(filename = "hist_ar1_D", plot = hist_ar1_D, path = "../Manuscript", height = 2.1, width = 6)
```

@@

# Generate histograms plot
hist_ma1_D <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")

@@

hist_ma1_D

@@

# Generate histograms plot
hist_arma_D <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")

@@

hist_arma_D

@@

# Generate histograms plot
hist_ar2_D <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")

@@

hist_ar2_D

@@

@@

    stat.b[i] <- ks.test(x.b, "pgev", shape = shape.b, scale = scale.b)$statistic
  }

@@

>>>>

results$histogram <- factor(results$histogram, levels = c("Naive", "Parametric", "Babu"))

@@

# Save the histogram figure
ggsave(filename = "hist_fitted.pdf", plot = hist_fitted, path = "../Manuscript", height = 2.1, width = 6)
```

@@

# Set variables
n <- 100
ar <- 0.5
counter <- 0
nrep <- 1000
B <- 1000
mean <- 0
sd <- 1

@@

results$histogram <- factor(results$histogram, levels = c("Naive", "Copula"))

@@

# Set variables
n <- 100
counter <- 0
nrep <- 1000
B <- 1000
ma <- 0.5
mean <- 0
sd <- 1

@@

# Set variables
n <- 100
counter <- 0
nrep <- 1000
B <- 1000
ar <- 0.5
ma <- 0.3
mean <- 0
sd <- 1

@@

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(ar = ar, 
                                                           ma = ma), 
                                                      rand.gen=rnorm, 
                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
                                                      n = n),
                                                mean = mean,
                                                sd = sd)$p.value)

@@

# Set variables
n <- 100
counter <- 0
nrep <- 1000
B <- 1000
b1 <- 0.5
b2 <- 0.3
mean <- 0
sd <- 1

@@

@@

@@

```{r AR(1) FD}
test_copula_FD <- function(x, dist, B) {

@@

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_FD(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), "pnorm", B = B))
counter <- 0

@@

results$histogram <- factor(results$histogram, levels = c("Super Naive", "Naive Parametric", "Copula"))

# Generate histograms plot
hist_ar1_FD <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")
hist_ar1_FD

@@

# Save the histogram figure
ggsave(filename = "hist_ar1_FD.pdf", plot = hist_ar1_FD, path = "../Manuscript", height = 2.1, width = 6)
```

@@

results$histogram <- factor(results$histogram, levels = c("Super Naive", "Naive Parametric", "Copula"))

# Generate histograms plot
hist_ma1_FD <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")

@@

hist_ma1_FD

# Save the histogram figure
ggsave(filename = "hist_ma1_FD.pdf", plot = hist_ma1_FD, path = "../Manuscript", height = 2.1, width = 6)
```

@@

results$histogram <- factor(results$histogram, levels = c("Super Naive", "Naive Parametric", "Copula"))

# Generate histograms plot
hist_arma_FD <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")

@@

hist_arma_FD

# Save the histogram figure
ggsave(filename = "hist_arma_FD.pdf", plot = hist_arma_FD, path = "../Manuscript", height = 2.1, width = 6)
```

@@

results$histogram <- factor(results$histogram, levels = c("Super Naive", "Naive Parametric", "Copula"))

# Generate histograms plot
hist_ar2_FD <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")

@@

hist_ar2_FD

# Save the histogram figure
ggsave(filename = "hist_ar2_FD.pdf", plot = hist_ar2_FD, path = "../Manuscript", height = 2.1, width = 6)
```

@@

results$histogram <- factor(results$histogram, levels = c("Super Naive", "Naive Parametric", "Copula"))

@@

    stat.b[i] <- ks.test(x.b, "pgev", loc.b, shape = shape.b, scale = scale.b)$statistic
  }

@@

```{r hist_ma1_arma_ar2_D}
load('results_ma1_D.RData')
model <- rep("MA(1)", 2000)
ma1 <- data_frame(results, new_col)

load('results_arma_D.RData')
model <- rep("ARMA(1, 1)", 2000)
arma <- data_frame(results, new_col)

load('results_ar2_D.RData')
model <- rep("AR(2)", 2000)
ar2 <- data_frame(results, new_col)

data <- rbind(ma1, arma, ar2)

data$model <- factor(data$model, levels = c("MA(1)", "ARMA(1, 1)", "AR(2)"))
data$histogram <- factor(data$histogram, levels = c("Naive", "Copula"))

# Generate histograms plot
hist_ma1_arma_ar2_D <- ggplot(data) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(histogram~model, scales = "free_y")
hist_ma1_arma_ar2_D

ggsave(filename = "hist_ma1_arma_ar2_D.pdf", plot = hist_ma1_arma_ar2_D, path = "../Manuscript", height = 4.2, width = 6)
```

```{r hist_gamma_gev_D}
load('results_gamma_D.RData')
model <- rep("Gamma", 2000)
gamma <- data_frame(results, model)

load('results_gev_D.RData')
model <- rep("GEV", 2000)
gev <- data_frame(results, model)

data <- rbind(gamma, gev)

data$model <- factor(data$model, levels = c("Gamma", "GEV"))
data$histogram <- factor(data$histogram, levels = c("Naive", "Copula"))

# Generate histograms plot
hist_gamma_gev_D <- ggplot(data) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(histogram~model, scales = "free_y")
hist_gamma_gev_D

ggsave(filename = "hist_gamma_gev_D.pdf", plot = hist_gamma_gev_D, path = "../Manuscript", height = 4.2, width = 6)
```

```{r hist_ma1_arma_ar2_FD}
load('results_ma1_FD.RData')
model <- rep("MA(1)", 3000)
ma1 <- data_frame(results, model)

load('results_arma_FD.RData')
model <- rep("ARMA(1, 1)", 3000)
arma <- data_frame(results, model)

load('results_ar2_FD.RData')
model <- rep("AR(2)", 3000)
ar2 <- data_frame(results, model)

data <- rbind(ma1, arma, ar2)

data$model <- factor(data$model, levels = c("MA(1)", "ARMA(1, 1)", "AR(2)"))
data$histogram <- factor(data$histogram, levels = c("Super Naive", "Naive Parametric", "Copula"))

# Generate histograms plot
hist_ma1_arma_ar2_FD <- ggplot(data) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(histogram~model, scales = "free_y")
hist_ma1_arma_ar2_FD

ggsave(filename = "hist_ma1_arma_ar2_FD.pdf", plot = hist_ma1_arma_ar2_FD, path = "../Manuscript", height = 4.2, width = 6)
```

```{r hist_gamma_gev_FD}
load('results_gamma_FD.RData')
model <- rep("Gamma", 3000)
gamma <- data_frame(results, model)

load('results_gev_FD.RData')
model <- rep("GEV", 3000)
gev <- data_frame(results, model)

data <- rbind(gamma, gev)

data$model <- factor(data$model, levels = c("Gamma", "GEV"))
data$histogram <- factor(data$histogram, levels = c("Super Naive", "Naive Parametric", "Copula"))

# Generate histograms plot
hist_gamma_gev_FD <- ggplot(data) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(histogram~model, scales = "free_y", ncol = 2)
hist_gamma_gev_FD

ggsave(filename = "hist_gamma_gev_FD.pdf", plot = hist_gamma_gev_FD, path = "../Manuscript", height = 4.2, width = 6)
```
